Clustering in a hyperbolic model of complex networks.

### 2019-05-28 concentration_argument.tex
included all comments from Nikolaos and made final changes. Ready for Tobias.

Note that since all three corollaries follow from Lemma~\ref{lem:concentration_argument}, Proposition~\ref{prop:concentration_argument_all} follows if we can prove that the conclusions from this lemma hold when we replace $\rho(y,k_n)$ with either $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$. For this the following, slightly more general version of Lemma~\ref{lem:concentration_argument} will be important.

Although powerful, the current versions of the concentration of heights arguments are only valid for the function $\rho(y,k_n) := \Prob{\Po\left(\Mu{\BallPo{y}}\right) = k_n}$, which uses the neighbourhoods in the infinite model $\Ginf$. Since we will also be working in the Poissonized KPKVB model $\GPo$ and the finite box model $\Gbox$, we would like to use concentration of heights arguments when the integrand contains either the function $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$. To establish these result we first prove a more general version of Lemma~\ref{lem:concentration_argument}.

\begin{lemma}\label{lem:concentration_argument_rho_approximation}
Let $\alpha > \frac{1}{2}, \nu > 0$ and $k_n \to \infty$ such that $k_n = \smallO{n}$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and define
\[
	\lambda_n^\pm = (\ell_n \pm C \sqrt{\ell_n \log(\ell_n)}) \wedge \xi, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi}\right).
\] 
In addition, let $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, with $\hat{\mu}_n(y) = (1 + \phi_n(y))\mu(y)$ and 
where $\phi_n(y)$ is a differentiable function satisfying:
\begin{enumerate}[\upshape i)]
\item For some $0 < \varepsilon < 1$, $\displaystyle \lim_{n \to \infty} \sup_{0 \le y \le (1 - \varepsilon)R} |\phi_n(y)| = 0$,
\item $\displaystyle \lim_{n \to \infty}  \sup_{y \in \Kcal_{C}(\ell_n)} |\phi_n^\prime(y)| = 0.$
\end{enumerate}
Then the following holds:
\begin{enumerate}
\item For any continuous function $h : \R_+ \rightarrow  \R$, such that $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$ for some $\beta < \alpha$, 
\begin{equation}\label{eq:error_bound_int_rho_approx_not_K}
	\int_{\R_+ \setminus (a_n^-, a_n^+)} \hat{\rho}_n(y,k_n) h(y) \alpha e^{-\alpha y} \dd y
	= \bigO{k_n^{-(1+C^2)/2}},
\end{equation}
as $n \to \infty$.
\item If in addition, $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$, as $n \to \infty$, then,
\begin{equation}\label{eq:concentration_h_rho_approx}
	\int_0^\infty h(y) \hat{\rho}_n(y,k_n) \alpha e^{-\alpha y} \dd y \sim  
		\int_0^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
\end{equation}
as $n \to \infty$.
\end{enumerate}
\end{lemma}

@@

\paragraph{Proof of statement 1.}
Let $0 < \varepsilon < 1$ be such that condition ii) holds and take $\varepsilon^\prime = \min\{\varepsilon,1/3\} < 1/2$. We first show that the integration over $(1-\varepsilon^\prime)R \le y \le R$ is negligible.

Since $h(y) = \bigO{e^{\beta y}}$ we have
\begin{align*}
	\int_{(1-\varepsilon^\prime)R}^{R} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
	&= \bigO{1} \hat{\rho}_n((1-\varepsilon^\prime)R,k_n) e^{-(\alpha-\beta)(1-\varepsilon^\prime)R} \\
	&= \bigO{\hat{\rho}_n((1-\varepsilon^\prime)R,k_n) n^{-2(\beta-\alpha)(1-\varepsilon^\prime)}}.
\end{align*}
By assumption on $\hat{\mu}_n(y)$ we have that $\hat{\mu}_n((1-\varepsilon^\prime)R) = \bigT{\mu((1-\varepsilon^\prime)R} = \bigT{n^{2(1-\varepsilon^\prime)}}$. Since $k_n = \smallO{n}$, by our choice of $\varepsilon^\prime$, $\hat{\mu}_n((1-\varepsilon^\prime)R)/k_n = \omega\left(n^{1 - 2\varepsilon^\prime}\right) \to \infty$ as $n \to \infty$. We can now use Stirling's approximation to bound $\hat{\rho}_n((1-\varepsilon^\prime)R,k_n)$ as
\begin{align*}
	\hat{\rho}_n((1-\varepsilon^\prime)R,k_n) &= \Prob{\Po(\hat{\mu}_n((1-\varepsilon^\prime)R)) = k_n} \\
	&= \frac{\hat{\mu}_n((1-\varepsilon^\prime)R)^{k_n}}{k_n!} e^{-\hat{\mu}_n((1-\varepsilon^\prime)R)}\\
	&= \bigO{1} k_n^{-1/2} \left(\frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)^{k_n} e^{k_n - \hat{\mu}_n((1-\varepsilon^\prime)R)}\\
	&= \bigO{1} k_n^{-1/2} e^{k_n\left(1 - \frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)+ \log\left(\frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)}\\
	&\le \bigO{1} k_n^{-1/2} e^{-\hat{\mu}_n((1-\varepsilon^\prime)R)/2},
\end{align*}
where the last line follows since $1 - x + \log(x) \le -x/2$ for large enough $x$. We conclude that
\[
	\int_{(1-\varepsilon^\prime)R}^{R} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
	= \bigO{k_n^{-1/2} n^{-2(\beta-\alpha)(1-\varepsilon^\prime)} e^{-n^{2(1-\varepsilon^\prime)}}}
	= \bigO{k_n^{(1+C^2)/2}}.
\]

We are left to show that for sufficiently large $C > 0$,
\begin{equation}\label{eq:concentration_argument_an_-}
	 \int_0^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = \bigO{k_n^{-(1+C^2)/2}},
\end{equation}
and
\begin{equation}\label{eq:concentration_argument_an_+}
	\int_{a_n^+}^{(1-\varepsilon^\prime)R} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = \bigO{k_n^{-(1+C^2)/2}}.
\end{equation}
%\TM{ Why can we change the upper limit of the integral? PLease elaborate (in the paper) }

For simplicity we write $\mu(y) := \mu\left(\BallPo{y}\right)$. Now fix some $0 < \delta < 1$ and let $n$ be large enough such that 
\[
\sup_{0 < y \le (1-\varepsilon^\prime)R} |\phi_n(y)| < \delta, \quad
\lambda_n^+(1 - \delta) > k_n \quad \text{and} \quad
\lambda_n^-(1 + \delta) < k_n.
\]

Next, recall that the function $\lambda \mapsto \Prob{\Po(\lambda) = k}$ is monotonic increasing on $[0,k]$ and monotonic decreasing on $[k, \infty)$. Then since for $n$ large enough we have 
\[
	\hat{\mu}_n(y) = \mu(y)(1 + \phi_n(y)) \ge \mu(y)(1 - \delta) \ge \mu(a_n^+)(1 - \delta)
	= (\ell_n + C \kappa_n)(1 - \delta) > k_n,
\]
it follows that 
\[
	\hat{\rho}_n(y,k_n) = \Prob{\Po(\hat{\mu}_n(y)) = k_n} \le \Prob{\Po(\mu(y)(1-\delta)) = k_n},
\]
for all $a_n^+ \le y \le (1-\varepsilon^\prime)R$. By making the change of variables $z = \mu^{-1}(\mu(y)(1-\delta)) = y + 2 \log(1-\delta)$ we then get
\begin{align*}
	\int_{a_n^+}^{(1-\varepsilon^\prime)R} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
	&\le \int_{a_n^+}^{(1-\varepsilon^\prime)R} \Prob{\Po(\mu(y)(1-\delta)) = k_n} 
		e^{(\beta-\alpha) y} \dd y\\
	&= (1-\delta)^{\beta - \alpha} \int_{a_n^+ + 2\log(1-\delta)}^{(1-\varepsilon^\prime)R + 2\log(1-\delta)} 
		\Prob{\Po(\mu(z)) = k_n} e^{(\beta - \alpha)z} \dd z\\
	&= \bigO{1} \int_{a_n^+}^{\infty} \rho(z,k_n) e^{(\beta - \alpha)z} \dd z\\
	&= \bigO{k_n^{-(1+C^2)/2}},
\end{align*}
where the last line is due to Lemma~\ref{lem:concentration_argument}. This proves~\eqref{eq:concentration_argument_an_+}.

%implies that for large enough $C$,
%\[
%	\lim_{n \to \infty} k_n^s \int_{a_n^+}^{\infty} \rho(z,k_n) e^{(\beta - \alpha)z} \dd z = 0,
%\]
%we have proven~\eqref{eq:concentration_argument_an_+}.

The proof of~\eqref{eq:concentration_argument_an_-} follows the same line of reasoning. This time we use that for $0 \le y \le a_n^-$,
\[
	\hat{\mu}_n(y) \le \mu(y)(1 + \delta) \ge \mu(a_n^-)(1 + \delta)
		= (\ell_n - C \kappa_n)(1 + \delta) < k_n,
\]
so that 
\[
	\hat{\rho}_n(y,k_n) = \Prob{\Po(\hat{\mu}_n(y)) = k_n} \le \Prob{\Po(\mu(y)(1+\delta)) = k_n}.
\]
Making a similar change of variables $z = y + 2 \log(1+\delta)$ we then get
\begin{align*}
	\int_0^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
	&= \int_0^{a_n^-}\Prob{\Po(\mu(y)(1-\delta)) = k_n} 
		e^{(\beta-\alpha) y} \dd y\\
	&\le (1+\delta)^{\beta - \alpha} \int_0^{a_n^- + 2\log(1+\delta)} 
		\rho(z,k_n) e^{(\beta - \alpha)z} \dd z,
\end{align*}
and hence~\eqref{eq:concentration_argument_an_-} follows by another application of Lemma~\ref{lem:concentration_argument}.

@@

The proof of the second statement follows the same line of reasoning as above. First, by the mean value theorem for definite integrals 
\[
	\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) h(y) e^{-\alpha y} \dd y
	= h(c_n) \int_{a_n^-}^{a_n^+} \rho(z,k_n) e^{-\alpha z} \dd z,
\]
for some $c_n \in (a_n^-, a_n^+)$. Since, $c_n \sim 2 \log(k_n/\xi)$, by assumption on $h$, $h(c_n)\sim h(2\log(k_n/\xi))$. Therefore it is enough to show that
\[
	\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
	= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(z,k_n) e^{-\alpha z} \dd z.
\] 
or equivalently,
\[
	\int_{a_n^-}^{a_n^+} \rho(z,k_n) e^{-\alpha z} \dd z
	= \left(1 + o(1)\right)\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y.
\]

Using the change of variable $z = \mu^{-1}(\hat{\mu}_n(y))$ and writing $\hat{a}_n^\pm = \hat{\mu}_n^{-1}(\mu(a_n^\pm))$, we get
\begin{align*}
	\int_{a_n^-}^{a_n^+} \rho(z,k_n) e^{-\alpha z} \dd z 
	&= \int_{a_n^-}^{a_n^+} \Prob{\Po(\mu(z)) = k_n} e^{-\alpha z} \dd z\\
	&= \int_{\hat{a}_n^-}^{\hat{a}_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} e^{-\alpha \mu^{-1}(\hat{\mu}_n(y))} 
		\frac{\hat{\mu}_n^\prime(y)}{\mu^\prime(\mu^{-1}(\hat{\mu}_n(y)))} \dd y,
\end{align*}
where the fraction in the last line follows from the chain rule and the fact that $(\mu^{-1})^\prime(t) = (\mu^\prime(\mu^{-1}(t)))^{-1}$.

Now recall that $\hat{\mu}_n(y) = \mu(y)(1 + \phi_n(y))$, with $\phi_n(y)$ satisfying conditions i) and ii). It then follows $\hat{\mu}_n^\prime(y) = (1 + \smallO{1})\mu^\prime(y)$ as $n \to \infty$, uniformly on $(a_n^-, a_n^+)$. Next we note that $\mu^\prime(y) = \mu(y)/2$ from which it follows that uniformly on $[a_n^-, a_n^+]$,
\[
	\frac{\hat{\mu}_n^\prime(y)}{\mu^\prime(\mu^{-1}(\hat{\mu}_n(y)))}
	= \frac{2\hat{\mu}_n^\prime(y)}{\hat{\mu}_n(y)}
	= \frac{(1 + \smallO{1})2\mu^\prime(y)}{(1 + \smallO{1})\mu(y)}
	= (1+\smallO{1})
\]
Therefore,
\begin{align*}
	\int_{a_n^-}^{a_n^+} \rho(z,k_n) e^{-\alpha z} \dd z
	&= (1 + \smallO{1})\int_{\hat{a}_n^-}^{\hat{a}_n^+} \Prob{\Po(\hat{\mu}_n(y)) = k_n} e^{-\alpha y} \dd y\\
	&= (1 + \smallO{1}) \int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y\\
	&= (1 + \smallO{1}) \int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
\end{align*}
which finishes the proof.
\end{proof}

To apply this lemma to $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$ we need to show that both these functions are of the form $\rho(y,k_n)(1 + \phi_n(y))$, where $\phi_n(y)$ satisfies the conditions i) and ii) in Lemma~\ref{lem:concentration_argument_rho_approximation}. We will do this in the next two sections and establish that the results from Corollaries~\ref{cor:concentration_of_heights_asymptotics}, \ref{cor:concentration_heights_bounds_n}
and~\ref{cor:concentration_heights_asymptotics_n} hold when we replace $\rho(y,k_n)$ with either $\rho_{\text{box}}(y,k_n)$
or $\rho_{\Po}(y,k_n)$.

@@

Let us now define
\[
	\rho_{\mathrm{box}}(y,k) = \Prob{\Po(\mu(\BallPon{y})) = k}.
\]
The following is then immediate.

\PvdH{Check if we need to define this earlier.}

>>>>

Although powerful, the current versions of the concentration of heights arguments are only valid for the function $\rho(y,k_n) := \Prob{\Po\left(\Mu{\BallPo{y}}\right) = k_n}$, which uses the neighbourhoods in the infinite model $\Ginf$. 
Since we will also be working in the Poissonized KPKVB model $\GPo$ and the finite box model $\Gbox$, we would like to use concentration of heights arguments for the degree distribution function in these models. To be more precise, let us define
\[
	\rho_{\Po}(y,k) = \Prob{\Po(\mu(\BallHyp{y})) = k}
\] 
and
\[
	\rho_{\mathrm{box}}(y,k) = \Prob{\Po(\mu(\BallPon{y})) = k}
\] 
Then we want when Lemma~\ref{lem:concentration_argument} to remain true if we replace $\rho(y,k_n)$ with either the function $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$. To establish these result we first prove a more general version of Lemma~\ref{lem:concentration_argument}.

\begin{lemma}\label{lem:concentration_argument_rho_approximation}
Let $\alpha > \frac{1}{2}, \nu > 0$ and $k_n \to \infty$ such that $k_n = \smallO{n}$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and define
\[
	\lambda_n^\pm = (\ell_n \pm C \sqrt{\ell_n \log(\ell_n)}) \wedge \xi, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi}\right).
\] 
In addition, let $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, where $\hat{\mu}_n(y)$ is a differentiable function that satisfies for some $0 < \varepsilon < 1$
\begin{align*}
	&\mathrm{i)} \, \lim_{n \to \infty} \sup_{0 \le y \le (1 - \varepsilon)R} \frac{\hat{\mu}_n(y)}{\mu(\BallPo{y})} = 1
	\quad \text{and}
	&&\mathrm{ii)} \, \lim_{n \to \infty}  \sup_{0 \le y \le (1 - \varepsilon)R} \frac{\hat{\mu}_n^\prime(y)}{\mu(\BallPo{y})} = \frac{1}{2}.
\end{align*}
%
%
% with $\hat{\mu}_n(y) = (1 + \phi_n(y))\mu(y)$ and 
%where $\phi_n(y)$ is a differentiable function satisfying:
%\begin{enumerate}[\upshape i)]
%\item For some $0 < \varepsilon < 1$, $\displaystyle \lim_{n \to \infty} \sup_{0 \le y \le (1 - \varepsilon)R} |\phi_n(y)| = 0$,
%\item $\displaystyle \lim_{n \to \infty}  \sup_{y \in \Kcal_{C}(\ell_n)} |\phi_n^\prime(y)| = 0.$
%\end{enumerate}
Then the following holds:
\begin{enumerate}
\item For any continuous function $h : \R_+ \rightarrow  \R$, such that $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$ for some $\beta < \alpha$, 
\begin{equation}\label{eq:error_bound_int_rho_approx_not_K}
	\int_{\R_+ \setminus (a_n^-, a_n^+)} \hat{\rho}_n(y,k_n) h(y) \alpha e^{-\alpha y} \dd y
	= \bigO{k_n^{-(1+C^2)/2}},
\end{equation}
as $n \to \infty$.
\item If in addition, $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$, as $n \to \infty$, then,
\begin{equation}\label{eq:concentration_h_rho_approx}
	\int_0^\infty h(y) \hat{\rho}_n(y,k_n) \alpha e^{-\alpha y} \dd y \sim  
		\int_0^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
\end{equation}
as $n \to \infty$.
\end{enumerate}
\end{lemma}

@@

For simplicity we write $\mu(y) := \mu\left(\BallPo{y}\right) = \xi e^{y/2}$ throughout the proof. Observe that $\mu^\prime(y) = \mu(y)/2$ and $\mu^{-1}(y z) = \mu^{-1(y)} + \mu^{-1}(z)$.

%We note that the statement will follow from Lemma~\ref{lem:concentration_argument} if we can show that
%\[
%	\int_0^R \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
%	= \left(1 + o(1)\right) \int_0^R \rho(z,k_n) e^{-\alpha z} \dd z.
%\] 
%or equivalently,
%\[
%	\int_0^R \rho(z,k_n) e^{-\alpha z} \dd z
%	= \left(1 + o(1)\right)\int_0^R \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y.
%\]
%
%We will do this in two steps.
%
%Therefore, what is left is to show that
%\[
%	\int_0^{(1-\varepsilon^\prime)R} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
%	= \left(1 + o(1)\right) \int_0^{(1-\varepsilon^\prime)R} \rho(z,k_n) e^{-\alpha z} \dd z.
%\] 
%or equivalently,
%\[
%	\int_0^{(1-\varepsilon^\prime)R} \rho(z,k_n) e^{-\alpha z} \dd z
%	= \left(1 + o(1)\right)\int_0^{(1-\varepsilon^\prime)R} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y.
%\]
%
%Using the change of variable $z = \mu^{-1}(\hat{\mu}_n(y))$ and writing $\hat{a}_n^\pm = \hat{\mu}_n^{-1}(\mu(a_n^\pm))$ and $\hat{R}_{\varepsilon^\prime} := \hat{\mu}_n^{-1}(\mu((1-\varepsilon^\prime)R))$, we get
%\begin{align*}
%	\int_{a_n^+}^{(1-\varepsilon^\prime)R} \rho(z,k_n) e^{-\alpha z} \dd z 
%	&= \int_{a_n^+}^{(1-\varepsilon^\prime)R} \Prob{\Po(\mu(z)) = k_n} e^{-\alpha z} \dd z\\
%	&= \int_{\hat{a}_n^+}^{\hat{R}_{\varepsilon^\prime}} \Prob{\Po(\hat{\mu}_n(y)) = k_n} e^{-\alpha \mu^{-1}(\hat{\mu}_n(y))} 
%		\frac{\hat{\mu}_n^\prime(y)}{\mu^\prime(\mu^{-1}(\hat{\mu}_n(y)))} \dd y,
%\end{align*}
%where the fraction in the last line follows from the chain rule and the fact that $(\mu^{-1})^\prime(t) = (\mu^\prime(\mu^{-1}(t)))^{-1}$.

\paragraph{Proof of statement 1.}

Let $0 < \varepsilon < 1$ be such that conditions i) and ii) hold, take $\varepsilon^\prime = \min\{\varepsilon/3,1/3\} < 1/2$ and let $\delta > 0$ be such that $\hat{\mu}_n(\delta) \ge \xi$. We first show that we can restrict to integration over $(\delta, (1-\varepsilon^\prime)R)$ that the integration over $(1-\varepsilon^\prime)R \le y \le R$ is negligible.

Since $h(y) = \bigO{e^{\beta y}}$ we have
\begin{align*}
	\int_{(1-\varepsilon^\prime)R}^{R} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
	&= \bigO{1} \hat{\rho}_n((1-\varepsilon^\prime)R,k_n) e^{-(\alpha-\beta)(1-\varepsilon^\prime)R} \\
	&= \bigO{\hat{\rho}_n((1-\varepsilon^\prime)R,k_n) n^{-2(\alpha-\beta)(1-\varepsilon^\prime)}}.
\end{align*}
By construction $\varepsilon^\prime < \varepsilon$, and hence by condition i) we have that $\hat{\mu}_n((1-\varepsilon^\prime)R) = \bigT{\mu((1-\varepsilon^\prime)R} = \bigT{n^{2(1-\varepsilon^\prime)}}$. Therefore, since $k_n = \smallO{n}$, it follows that $\hat{\mu}_n((1-\varepsilon^\prime)R)/k_n = \omega\left(n^{1 - 2\varepsilon^\prime}\right) \to \infty$ as $n \to \infty$. We can now use Stirling's approximation to bound $\hat{\rho}_n((1-\varepsilon^\prime)R,k_n)$ as
\begin{align*}
	\hat{\rho}_n((1-\varepsilon^\prime)R,k_n) &= \Prob{\Po(\hat{\mu}_n((1-\varepsilon^\prime)R)) = k_n} \\
	&= \frac{\hat{\mu}_n((1-\varepsilon^\prime)R)^{k_n}}{k_n!} e^{-\hat{\mu}_n((1-\varepsilon^\prime)R)}\\
	&= \bigO{1} k_n^{-1/2} \left(\frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)^{k_n} e^{k_n - \hat{\mu}_n((1-\varepsilon^\prime)R)}\\
	&= \bigO{1} k_n^{-1/2} e^{k_n\left(1 - \frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)+ \log\left(\frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)}\\
	&\le \bigO{1} k_n^{-1/2} e^{-\hat{\mu}_n((1-\varepsilon^\prime)R)/2},
\end{align*}
where the last line follows since $1 - x + \log(x) \le -x/2$ for large enough $x$. We conclude that
\[
	\int_{(1-\varepsilon^\prime)R}^{R} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
	= \bigO{k_n^{-1/2} n^{-2(\beta-\alpha)(1-\varepsilon^\prime)} e^{-n^{2(1-\varepsilon^\prime)}}}
	= \bigO{k_n^{-(1+C^2)/2}}.
\]

In a similar fashion we get that
\begin{align*}
	\int_0^\delta h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
	&= \bigO{1} \hat{\rho}_n(\delta, k_n) \\
	&= \bigO{1} k_n^{-1/2} e^{-k_n(\log(k_n)-\hat{\mu}_n(\delta))} = \bigO{k_n^{-(1+C^2)/2}}.
\end{align*}

We are thus left to show that for sufficiently large $C > 0$,
\begin{equation}\label{eq:concentration_argument_an_-}
	 \int_\delta^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = \bigO{k_n^{-(1+C^2)/2}},
\end{equation}
and
\begin{equation}\label{eq:concentration_argument_an_+}
	\int_{a_n^+}^{(1-\varepsilon^\prime)R} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = \bigO{k_n^{-(1+C^2)/2}}.
\end{equation}
To prove this we first establish a result that will also help with proving statement 2.

Let $(a, b) \subseteq (\delta,(1-\varepsilon^\prime)R)$ and consider the change of variable $z = \mu^{-1}(\hat{\mu}_n(y))$. Then, writing $\hat{a} = \hat{\mu}_n^{-1}(\mu(a))$ and similar for $\hat{b}$, we get
\begin{align*}
	\int_{a}^{b} \rho(z,k_n) e^{-\alpha z} \dd z 
	&= \int_{a}^{b} \Prob{\Po(\mu(z)) = k_n} e^{-\alpha z} \dd z\\
	&= \int_{\hat{a}}^{\hat{b}} \Prob{\Po(\hat{\mu}_n(y)) = k_n} e^{-\alpha \mu^{-1}(\hat{\mu}_n(y))} 
		\frac{\hat{\mu}_n^\prime(y)}{\mu^\prime(\mu^{-1}(\hat{\mu}_n(y)))} \dd y,
\end{align*}
where the fraction in the last line follows from the chain rule and the fact that $(\mu^{-1})^\prime(t) = (\mu^\prime(\mu^{-1}(t)))^{-1}$.

Now recall that $\hat{\mu}_n(y)$ satisfies conditions i) and ii). Since $\mu^\prime(y) = \mu(y)/2$ it follows that, uniformly on $(a,b)$,
\[
	\frac{\hat{\mu}_n^\prime(y)}{\mu^\prime(\mu^{-1}(\hat{\mu}_n(y)))}
	= \frac{2\hat{\mu}_n^\prime(y)}{\hat{\mu}_n(y)}
	= \frac{(1 + \smallO{1})2\hat{\mu}_n^\prime(y)}{(1 + \smallO{1})\mu(y)}
	= (1+\smallO{1}).
\]
Moreover, we have
\[
	e^{-\alpha \mu^{-1}(\hat{\mu}_n(y))} = e^{-\alpha (y + \mu^{-1}(1+\smallO{1}))} = (1+\smallO{1})e^{-\alpha y},
\]
uniformly on $(a,b)$. These results then imply
\begin{equation}\label{eq:equivalence_integral_rho_change_variables}
	\int_{a}^{b} \rho(z,k_n) e^{-\alpha z} \dd z 
	= (1+\smallO{1}) \int_{\hat{a}}^{\hat{b}} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y.
\end{equation}

Now, using~\eqref{eq:equivalence_integral_rho_change_variables} with $a = \mu^{-1}(\hat{\mu}_n(\delta))$ and $b = \mu^{-1}(\hat{\mu}_n(a_n^-)$ we get
\begin{align*}
	\int_a^b \rho(y,k_n) e^{(\beta-\alpha) y} \dd y
	&= (1+\smallO{1}) \int_{\delta}^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y.
\end{align*}
Since $\mu^{-1}(\hat{\mu}_n(a_n^-) = (1+\smallO{1})a_n^-$ and $b \ge 0$ the left hand side is
\[
	\bigO{1} \int_0^{a_n^-} \rho(y,k_n) e^{(\beta-\alpha) y} \dd y,
\]
and hence~\eqref{eq:concentration_argument_an_-} follows from Lemma~\ref{lem:concentration_argument}. The proof of~\eqref{eq:concentration_argument_an_+} follows in a similar way.

@@

The proof of the second statement follows the same line of reasoning as above, using~\eqref{eq:equivalence_integral_rho_change_variables}. First, the mean value theorem for definite integrals implies that
\[
	\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) h(y) e^{-\alpha y} \dd y
	= h(c_n) \int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y,
\]
for some $c_n \in (a_n^-, a_n^+)$. Since, $c_n \sim 2 \log(k_n/\xi)$, by assumption on $h$, $h(c_n)\sim h(2\log(k_n/\xi))$. 
Therefore it is enough to show that
\[
	\int_{a_n^-}^{a_n^+} \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
	= \left(1 + o(1)\right) \int_{a_n^-}^{a_n^+} \rho(z,k_n) e^{-\alpha z} \dd z.
\] 
This however follows immediately from~\eqref{eq:equivalence_integral_rho_change_variables} by picking $a = \mu^{-1}(\hat{\mu}_n(a_n^-))$ and $b = \mu^{-1}(\hat{\mu}_n(a_n^+))$.
\end{proof}

To apply this lemma to $\rho_{\Po}(y,k_n)$ or $\rho_{\text{box}}(y,k_n)$ we need to show that both these functions satisfies the conditions i) and ii) in Lemma~\ref{lem:concentration_argument_rho_approximation}. We will do this in the next two sections and establish that the results from Corollaries~\ref{cor:concentration_of_heights_asymptotics}, \ref{cor:concentration_heights_bounds_n}
and~\ref{cor:concentration_heights_asymptotics_n} hold when we replace $\rho(y,k_n)$ with either $\rho_{\text{box}}(y,k_n)$
or $\rho_{\Po}(y,k_n)$.

@@

From the definition of $\phi_n(y)$ in Lemma~\ref{lem:average_degree_P_n} it is immediate that $\rho_{\mathrm{box}}(y,k)$ satisfies the conditions for $\hat{\rho}_n(y,k)$ in Lemma~\ref{lem:concentration_argument_rho_approximation}. We thus have the following corollary.
